### 2015-04-09 rscripts/data_review.Rmd
a little more DRY, reorg

```{r, echo=FALSE}
censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
][,
  login_day := login %/% (24*60*60)
][,
  logout_day := logout %/% (24*60*60)
][,
  login_time := login - login_day*24*60*60
][,
  logout_time := logout - logout_day*24*60*60
][,
  run_id := 0
][,
  sample_id := 0
][,
  target := FALSE
]
setkey(censor.dt, run_id, sample_id, login_day, login_time, logout_day, logout_time, user_id, location_id)
save(censor.dt, file = "../input/censored.Rdata")
```

>>>>

```{r, echo=FALSE}
breakoutDays <- function(dt) {
  dt[,
    user_id := .GRP, by=user_id
  ][,
    location_id := .GRP, by=location_id
  ][,
    login_day := login %/% (24*60*60)
  ][,
    logout_day := logout %/% (24*60*60)
  ][,
    login_time := login - login_day*24*60*60
  ][,
    logout_time := logout - logout_day*24*60*60
  ]
}
breakoutDays(censor.dt[,
  user_id := .GRP, by=user_id
][,
  location_id := .GRP, by=location_id
][,
  run_id := 0
][,
  sample_id := 0
][,
  target := FALSE
])
setkey(censor.dt, run_id, sample_id, login_day, login_time, logout_day, logout_time, user_id, location_id)
save(censor.dt, breakoutDays, file = "../input/censored.Rdata")
```
